---
title: |
       | Electornic supplemnt: 
       | A Seismologically Consistent Surface Rupture Length Model for 
       | Unbounded and Width-Limited Events
always_allow_html: true
date: "`r Sys.Date()`"
author: |
 | G. Lavrentiadis, UCLA & Caltech 
 | Y. Wang,  USC 
 | N.A. Abrahamson, UC Berkeley 
 | Y. Bozorgnia, UCLA 
 | C. Goulet, USC
output: html_document
---

<style type="text/css">

h1.title {
  font-size: 25px;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load libraries
# library(REdaS)
library(pracma)
library(tidyverse)
#library(reshape2)
library(kableExtra)
#regression libraries
library(lme4)
library(nlsr)
#plotting libraries
library(ggplot2)
library(RColorBrewer)
library(scales)
#user functions
and.array   <- function (...)  Reduce("&", list(...))

#set plotting info
base_breaks <- function(n = 10){
  function(x) {
    axisTicks(log10(range(x, na.rm = TRUE)), log = TRUE, n = n)
  }
}

#log breaks
breaks_log       <- 10^(-10:10)
breaks_log_minor <- rep(1:9, 21)*(10^rep(-10:10, each=9))

#plotting theme
theme_set(theme_linedraw())
```

## Introduction 
This study presents a new $SRL$ model with physically defensible scaling for unbounded and width-limited ruptures.

Study Objectives:

* Consistent scaling with seismological theory
* Captures scaling for width-limited ruptures

## Load Data

```{r define_var, echo=FALSE}
#SRL flatfiles
#FDHI
fname_FDHI_srl <- '../Data/flatfiles/event_rupture_length_augmented.csv'
#SCEC
fname_SCEC_srl_original  <- '../Data/SCEC/Original_summary_srl.csv'
fname_SCEC_srl_low_width <- '../Data/SCEC/Lower_width_summary_srl.csv'
fname_SCEC_srl_const_sig <- '../Data/SCEC/Constant_stress_summary_srl.csv'
fname_SCEC_srl_sim2      <- '../Data/SCEC/Simulations2_srl.csv'
fname_SCEC_srl_sim3      <- '../Data/SCEC/Simulations3_srl.csv'
fname_SCEC_srl_sim4      <- '../Data/SCEC/Simulations4_srl.csv'

#output directory 
dir_out <- '../Data/SRL_model/'
dir_fig <- file.path(dir_out, 'figures/')

#text size
size_title <- 13
size_text  <- 12

#create output directories
dir.create(dir_out, showWarnings = FALSE)
dir.create(dir_fig, showWarnings = FALSE)
```

The empirical data that are used in model development include the FDHI (Sarmiento et al. 2021), Wells and Coppersmith (1994), and Baize et al. (2020) datasets. 
The surface rupture lengths ($SRL$) of the events in FDHI dataset are computed based on the Event Coordinate System (ECS), while the $SRL$ in Wells and Coppersmith (1994) and Baize et al. (2020) are reported directly. 
Additionally, dynamic rupture simulations performed by SCEC are used to derive the rupture width model for the width-limited ruptures. 

```{r load_data}
#read srl flatfiles
#FDHI
df_FDHI_srl_all <- read.csv(fname_FDHI_srl)

#FDHI processing
#create normal and reverse fault flags
df_FDHI_srl_all$FN <- pmax(-df_FDHI_srl_all$sof, 0)
df_FDHI_srl_all$FR <- pmax( df_FDHI_srl_all$sof, 0)
df_FDHI_srl_all$FD <- abs(  df_FDHI_srl_all$sof )
#style of faulting name
df_FDHI_srl_all$style2                         <- 'Strike-Slip'
df_FDHI_srl_all[df_FDHI_srl_all$FN>0,'style2'] <- 'Normal'
df_FDHI_srl_all[df_FDHI_srl_all$FR>0,'style2'] <- 'Reverse'
#fault width
df_FDHI_srl_all$seis_width <- df_FDHI_srl_all$seis_depth / sin(deg2rad(df_FDHI_srl_all$dip))

#SCEC
#read srl flatfiles
df_SCEC_srl_original  <- read.csv(fname_SCEC_srl_original)
df_SCEC_srl_low_width <- read.csv(fname_SCEC_srl_low_width)
df_SCEC_srl_const_sig <- read.csv(fname_SCEC_srl_const_sig)
df_SCEC_srl_sim_2     <- read.csv(fname_SCEC_srl_sim2)
df_SCEC_srl_sim_3     <- read.csv(fname_SCEC_srl_sim3)
df_SCEC_srl_sim_4     <- read.csv(fname_SCEC_srl_sim4)

#SCEC processing
#define seimogenic depths
df_SCEC_srl_original$seis_depth  <- 20
df_SCEC_srl_low_width$seis_depth <- 15 
df_SCEC_srl_const_sig$seis_depth <- 20
df_SCEC_srl_sim_2$seis_depth     <- 20
df_SCEC_srl_sim_3$seis_depth     <- 20 
df_SCEC_srl_sim_4$seis_depth     <- 20 
#merged data-frame of different simulations
df_SCEC_srl <- bind_rows( df_SCEC_srl_original, df_SCEC_srl_low_width, df_SCEC_srl_const_sig,
                          df_SCEC_srl_sim_2, df_SCEC_srl_sim_3, df_SCEC_srl_sim_4)
#identify width limited events
df_SCEC_srl$flag_wlim <- FALSE
df_SCEC_srl[df_SCEC_srl$wef >= df_SCEC_srl$seis_depth-2.5,'flag_wlim'] <- TRUE 
rm(list=c('df_SCEC_srl_original','df_SCEC_srl_low_width','df_SCEC_srl_const_sig',
          'df_SCEC_srl_sim_2', 'df_SCEC_srl_sim_3', 'df_SCEC_srl_sim_4'))
```

The maximum fault width of the empirical data was calculated based on the thickness of the seismogenic zone ($D_{seis}$) and fault dip angle ($\theta$).
Table 1 summarizes $D_{seis}$ based on the fault location and Table 2 summarizes $\theta$ for different styles of faulting. 
$$
  W_{lim} = \frac{D_{seis}}{\sin(\theta)}
$$
$W_{lim}$ is the maximum width a rupture can reach before it becomes width limited. 


```{r, tab1, echo=FALSE}
df <- data.frame(regions = c("California", "Guatemala", "New Zealand", "Indonesia", "Japan", "Himalayan Region", "Australia","Other"),
                 seis_depth = c(15, 15, 15, 15, 17, 30, 40, 22))
kable(df, col.names = c("Region", "Seismogenic Depth (km)"),  caption = "Table 1. Seismogenic Zone Thickness for Differnt Regions") %>%
  kable_styling(latex_options = "hold_position")
```

```{r, tab2, echo=FALSE}
df <- data.frame(sof = c("Strike-Slip", "Normal", "Reverse"),
                 dip = c(90, 60, 45))
kable(df, col.names = c("Style of Fauling", "Dip Angle (deg)"),  caption = "Table 2. Dip Angles for Differnt Styles of Faulting") %>%
  kable_styling(latex_options = "hold_position")
```


### Outliers

The following events were excluded from the regression dataset:

* Events less than $\mathbf{M}~5$
* 1892 Laguna Salada: it was occurred in 1892 but mapped in the 2010s. Magnitude is estimated.
* 1978 IzuOshima: surface is incomplete, rupture probably extended offshore to southeast; epicenter is offshore ~17 km
* 1993 Killari: it occurred in a stable continental region; probably a lot of deformation accommodated via folding/warping that was unmapped

```{r outliers}
#events for regression
df_FDHI_srl <- df_FDHI_srl_all
#remove outliers 
df_FDHI_srl  <- subset(df_FDHI_srl, !is.na(event_len) & flag_missing==0 & flag_multiple==0 )
#1892 Laguna Salada
df_FDHI_srl  <- subset(df_FDHI_srl, !(EQ_ID==40 & FLT_ID==1))
#1978 IzuOshima
df_FDHI_srl  <- subset(df_FDHI_srl, !EQ_ID==62)
#1993 Killari
df_FDHI_srl  <- subset(df_FDHI_srl, !EQ_ID==74)


#remove mag less than 5
df_FDHI_srl  <- subset(df_FDHI_srl, magnitude>=5)

#summarize all outliers
df_FDHI_srl_out <- subset(df_FDHI_srl_all,!(rownames(df_FDHI_srl_all)%in%rownames(df_FDHI_srl)))
```

### Summary datasets

```{r data_set_fig, echo=FALSE}
#color palette
color_sof     <- c('#E69F00', '#56B4E9', '#009E73')
color_emp_sim <- c("#0072B2", "#D55E00")


#srl vs mag FDHI
pl_data_len_mag <- ggplot() + geom_point(data=df_FDHI_srl, aes(x=magnitude, event_len, shape=style2, color=style2, size=as.factor(FLT_ID))) +
                              scale_shape_manual(values=c(19,15,17))+
                              scale_color_manual(values=color_sof) +
                              scale_size_manual(values=c(1.4,2,2.4), labels=c('FDHI (2021)','W&C (1994)','Baize et al. (2020)')) +
                              xlim(4.5, 8.5) + 
                              scale_y_log10(breaks=breaks_log,  minor_breaks=breaks_log_minor,
                                            labels=trans_format("log10", math_format(10^.x)), 
                                            limits=c(1, 10^3)) +
                              annotation_logticks(sides = "l") + 
                              labs(x='Magnitude', y='Surface Rupture Length (km)', color='Fault Style', shape='Fault Style', size='Dataset') +
                              theme(plot.title=element_text(size=size_title), axis.title=element_text(size=size_title), 
                                    axis.text.y=element_text(size=size_text), axis.text.x=element_text(size=size_text),
                                    legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

#srl vs mag FDHI
pl_data_FDHI_SCEC_cmp <- ggplot() + geom_point(data=df_FDHI_srl, aes(x=magnitude, event_len, 
                                                                     shape=as.factor('Empirical'), color=as.factor('Empirical'),
                                                                     size=as.factor('Empirical'))) +
                                    geom_point(data=df_SCEC_srl, aes(x=magnitude, rup_srl_wide, 
                                                                     shape=as.factor('SCEC -\nSimulations'),
                                                                     color=as.factor('SCEC -\nSimulations'),
                                                                     size=as.factor('SCEC -\nSimulations'))) +
                                    scale_shape_manual(values=c(19,15,17))+
                                    scale_color_manual(values=color_emp_sim) +
                                    scale_size_manual(values = c(2.2,1.6)) +
                                    xlim(4.5, 8.5) + 
                                    scale_y_log10(breaks=breaks_log,  minor_breaks=breaks_log_minor,
                                                  labels=trans_format("log10", math_format(10^.x)), 
                                                  limits=c(1, 10^3)) +
                                    annotation_logticks(sides = "l") + labs(x='Magnitude', y='Surface Rupture Length (km)', 
                                                                            color='Dataset',  shape='Dataset', size='Dataset') +
                                    theme(plot.title=element_text(size=size_title), axis.title=element_text(size=size_title), 
                                          axis.text.y=element_text(size=size_text), axis.text.x=element_text(size=size_text),
                                          legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

#save figures
ggsave(file.path(dir_fig,'data_srl_mag_FDHI.png'),      plot=pl_data_len_mag,       device='png', width=6.6, height=4)
ggsave(file.path(dir_fig,'data_srl_mag_FDHI-SCEC.png'), plot=pl_data_FDHI_SCEC_cmp, device='png', width=6.3, height=4)
```

Summary statistics of the empirical dataset are presented below:
```{r, echo=FALSE, summary_emp_data}
#FDHI info
#number of events
fprintf('Number of Events per dataset:
        \t Total: %i
        \t FDHA: %i
        \t W&C: %i
        \t Baize: %i\n',
        nrow(df_FDHI_srl), sum(df_FDHI_srl$FLT_ID==1), sum(df_FDHI_srl$FLT_ID==2), sum(df_FDHI_srl$FLT_ID==3))
#number of different styles of faulting
fprintf('Number of Events per Style of Faulting:
        \t Strike-slip: %.0f
        \t Normal: %.0f
        \t Reverse: %.0f\n',
        sum(1-df_FDHI_srl$FD), sum(df_FDHI_srl$FN), sum(df_FDHI_srl$FR))
#magnitude range
fprintf('Magnitude Range:
        \t maximum: %.1f
        \t minimum: %.1f\n',
        max(df_FDHI_srl$magnitude), min(df_FDHI_srl$magnitude))
#rupture length range
fprintf('Rupture-Length Range:
        \t maximum: %.1f
        \t minimum: %.1f\n',
        max(df_FDHI_srl$event_len), min(df_FDHI_srl$event_len))
```

Figure 1 shows the Magnitude - Surface rupture length ($\mathbf{M} - SRL$) distribution of the empirical dataset.

```{r fig_data_mag_len, echo=FALSE, fig.cap="Figure 1. Magnitude - SRL distribution of selected empirical data"}
pl_data_len_mag
```

Summary statistics of the SCEC simulations are presented below:
```{r, echo=FALSE, summary_SCEC_data}
#SCEC info
#number of events
fprintf('Total number of simulations: %i\n', nrow(df_SCEC_srl))
#magnitude range
fprintf('Magnitude Range:
        \t maximum: %.1f
        \t minimum: %.1f\n',
        max(df_SCEC_srl$magnitude), min(df_SCEC_srl$magnitude))
#rupture length range
fprintf('Rupture-Length Range:
        \t maximum: %.1f
        \t minimum: %.1f\n',
        max(df_SCEC_srl$rup_srl_wide), min(df_SCEC_srl$rup_srl_wide))
```
Figure 2 compares the $\mathbf{M} - SRL$ distribution of empirical data and SCEC simulations. 
The two datasets show similar scaling supporting that the scaling relationships derived from the SCEC simulations are applicable to the empirical data. 

```{r fig_data_mag_len_scec_all, echo=FALSE, fig.cap="Figure 2. Comparison of Magnitude - SRL distribution of empirical data and SCEC simulations"}
pl_data_FDHI_SCEC_cmp
```

## Model Development

### Rupture Width Modeling Based on SCEC Simulations

The SCEC simulations were used to develop a Magnitude - Rupture width model for unbounded and width-limited ruptures.
Two models were evaluated: (i) a linear model between $W - \mathbf{M}$, hereafter denoted as ``model w0``, and (ii) a model with a scaling break at $W_{lim}$, hereafter denoted as ``model w1``

The functional form for ``model_w0`` is:
\begin{equation}
  \log(W) = \mathbf(M) + \epsilon_W
\end{equation}

The functional form for ``model_w1`` is:
\begin{equation}
log(W) = \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})) + \epsilon_W
\end{equation}

```{r width_model_mag_sec}
## Regression formulas
form_model_w0 <- log10(wef) ~ 1 + magnitude
form_model_w1 <- log10(wef) ~ 1 + magnitude

## Regression
fit_model_w0 <- lm(form_model_w0, data=df_SCEC_srl)
fit_model_w1 <- lm(form_model_w1, data=subset(df_SCEC_srl, !flag_wlim))
```

The $W - \mathbf{M}$ model summary is presented below. 
``model w1`` has a higher log likelihood and lower Akaike information criterion.


```{r, width_model_mag_sec_summary, echo=FALSE}
#residuals
res_model_w1     <- residuals(fit_model_w1)
res_model_w1_all <- log10(df_SCEC_srl$wef) - pmin( predict(fit_model_w1, df_SCEC_srl), log10(df_SCEC_srl$seis_depth) )

#coefficients
df_SCEC_model_width_mag_coeffs <-                                           as.data.frame(t(coef(fit_model_w0)), row.names='model_w0')
df_SCEC_model_width_mag_coeffs <- bind_rows(df_SCEC_model_width_mag_coeffs, as.data.frame(t(coef(fit_model_w1)), row.names='model_w1'))
df_SCEC_model_width_mag_coeffs['model_w0','sigma']   <- sigma(fit_model_w0)
df_SCEC_model_width_mag_coeffs['model_w1','sigma']   <- sigma(fit_model_w1)
colnames(df_SCEC_model_width_mag_coeffs) <- c('intrcp','M','sigma')

## Prediction
#initialize dataframe
df_SCEC_predict_width_mag <- data.frame(magnitude=linspace(4.5, 8.5, 100))
#predictions
df_SCEC_predict_width_mag$w0   <- 10^( predict(fit_model_w0, df_SCEC_predict_width_mag) )
df_SCEC_predict_width_mag$w1d1 <- pmin( 10^( predict(fit_model_w1, df_SCEC_predict_width_mag) ), 15)
df_SCEC_predict_width_mag$w1d2 <- pmin( 10^( predict(fit_model_w1, df_SCEC_predict_width_mag) ), 20)

#save width scaling coefficients
write.csv(df_SCEC_model_width_mag_coeffs,  file=file.path(dir_out, 'model_coeffs_width_mag_SCEC.csv'))

# comparison
#likelihood and aic comparison
fprintf('Width Modeling\n
         \tModel0:\n\t\tLogLik: %.2f\n\t\tAIC: %.2f\n
         \tModel1:\n\t\tLogLik: %.2f\n\t\tAIC: %.2f\n', 
         logLik(fit_model_w0), AIC(fit_model_w0),
         sum(log(dnorm(res_model_w1_all, sd=sigma(fit_model_w1)))), 2*3 - 2*sum(log(dnorm(res_model_w1_all, sd=sigma(fit_model_w1)))) )
```
The best estimates of the coefficients of the two candidate models are summarized in Table 3.

```{r, width_model_mag_coeffs, echo=FALSE}
#coefficients
kable(df_SCEC_model_width_mag_coeffs, 
      col.names = c('Intercept','$\\mathbf{M}$ scaling','$\\sigma$'),  
      caption = "Table 3. Rupture Width Model Coefficients") %>%
  kable_styling(latex_options = "hold_position")
```

Figure 3 compares the two candidate models against the SCEC simulations. 

```{r, width_models_mag_fig, echo=FALSE, fig.cap="Figure 3. Comparison of candidate rupture width models against the SCEC simulations"}
#color palette
color_width_flag <- c('#00BFC4', '#F8766D')
shape_width_flag <- c(15,1)

#figures predictions
pl_models_wlim_mag <- ggplot() + geom_point(data=df_SCEC_srl, aes(x=magnitude, y=wef,  color=flag_wlim, shape=flag_wlim)) +
                                 geom_line(data=df_SCEC_predict_width_mag, aes(x=magnitude, y=w0,   linetype=as.factor('Model w0: Linear')),        size=0.8) +
                                 geom_line(data=df_SCEC_predict_width_mag, aes(x=magnitude, y=w1d1, linetype=as.factor('Model w1: Width Limited')), size=0.8) +
                                 geom_line(data=df_SCEC_predict_width_mag, aes(x=magnitude, y=w1d2, linetype=as.factor('Model w1: Width Limited')), size=0.8) +
                                 scale_y_log10(breaks=trans_breaks("log10", function(x) 10^x), labels=trans_format("log10", math_format(10^.x))) +
                                 scale_linetype_manual(values=c("dashed", "solid"))+
                                 scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                                 scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                                 annotation_logticks(sides = "y") + 
                                 labs(x='Magnitude', y='Rupture Width (km)', linetype='Model', color='Width Limited', shape='Width Limited') + 
                                 xlim(4.5, 8.5) + 
                                 theme(plot.title=element_text(size=size_title), axis.title=element_text(size=size_title), 
                                       axis.text.y=element_text(size=size_text), axis.text.x=element_text(size=size_text),
                                       legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))
pl_models_wlim_mag
```

The summary of the ``model w1`` regression is provided below: 
```{r, width_model_1_summary}
summary(fit_model_w1)
```

Figure 4 shows the scaling of the preferred model (``model w1``) against the SCEC data. 

```{r width_model_mag_pref_fig, echo=FALSE, fig.cap="Figure 4. Preferred model for rupture width scaling"}

#figures predictions
pl_model_pref_wlim_mag <- ggplot() + geom_point(data=df_SCEC_srl, aes(x=magnitude, y=wef,  color=flag_wlim, shape=flag_wlim)) +
                                     geom_line(data=df_SCEC_predict_width_mag, aes(x=magnitude, y=w1d1), size=0.8, linetype="dashed") +
                                     geom_line(data=df_SCEC_predict_width_mag, aes(x=magnitude, y=w1d2), size=0.8) +
                                     scale_y_log10(breaks=trans_breaks("log10", function(x) 10^x), labels=trans_format("log10", math_format(10^.x))) +
                                     scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                                     scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                                     labs(x='Magnitude', y='Rupture Width (km)', linetype='Simulations', color='Events', shape='Events') +
                                     annotation_logticks(sides = "y") + xlim(4.5, 8.5) + 
                                     theme(plot.title=element_text(size=size_title), axis.title=element_text(size=size_title), 
                                           axis.text.y=element_text(size=size_text), axis.text.x=element_text(size=size_text),
                                           legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))
pl_model_pref_wlim_mag

#save figures
ggsave(file.path(dir_fig,'model_preferred_wlim_mag_SCEC.png'), plot=pl_model_pref_wlim_mag, device='png', width=6.5, height=4)
```

Figure 5 shows the residuals of the preferred model versus magnitude.

```{r, width_model_mag_pref_res_fig, echo=FALSE, fig.cap="Figure 5. Resisuals of Preferred Rupture Width Model for SCEC simulations"}

#figures predictions
pl_model_pref_wlim_mag_res <- ggplot(data=df_SCEC_srl, aes(x=magnitude, y=res_model_w1_all)) +
                                geom_point(aes(shape=flag_wlim,  color=flag_wlim)) +
                                geom_hline(yintercept=0,linetype="dashed") +
                                scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                                scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                                labs(x='Magnitude', y='Rupture Width residuals', 
                                     linetype='Simulations', color='Events', shape='Events') +
                                xlim(c(4.5, 8.5)) + ylim(c(-.2,.2)) + 
                                theme(plot.title=element_text(size=size_title), axis.title=element_text(size=size_title), 
                                      axis.text.y=element_text(size=size_text), axis.text.x=element_text(size=size_text),
                                      legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))
pl_model_pref_wlim_mag_res

#save figures
ggsave(file.path(dir_fig,'model_preferred_wlim_mag_SCEC_res.png'), plot=pl_model_pref_wlim_mag_res, device='png', width=6.5, height=4)
```

### SRL Model Derivation 

This section presents the deviation of the $SRL\sim\mathbf{M}$ functional form.
The Seismic Moment ($M_0$) is defined as:

\begin{equation}
M_0 = \mu~\bar{D}~L~W
\end{equation}

where $\mu$ is the stiffness of the crust, $\bar{D}$ is the average slip on the rupture, $L$ is the length of the rupture, and $W$ is width of the rupture. 
Taking the log of the previous equation and substituting the definition of the Moment Magnitude ($\mathbf{M} = \frac{2}{3}\log(M_0) - 10.7$) we get:

\begin{equation}
\mathbf{M} = \frac{2}{3}\log(\mu) + \frac{2}{3}\log(\bar{D}) + \frac{2}{3}\log(L) + \frac{2}{3}\log(W) - 10.7
\end{equation}

Since stiffness of the crust ($\mu$) is constant, the previous equation simplifies to:

\begin{equation}
\mathbf{M} =  \frac{2}{3}\log(\bar{D}) + \frac{2}{3}\log(L) + \frac{2}{3}\log(W) + c
\end{equation}

where $c$ is used to denote any arbitrary constant. 

Three commonly used scaling models for the average displacements found in the literature include the $\sqrt{A}$ model, hereafter called ``model 1``, the $W$ model, hereafter called ``model 2``, and the $L$ model, hereafter called ``model 3`` (Scholz, 1982; Romanowicz, 1992; Romanowicz and Rundle, 1993; Romanowicz, 1994; Scholz, 1994; Bodin and Brune, 1996; Pegler and Das, 1996; Scholz, 1997, 1998; Hanks and Bakun, 2002; Leonard, 2010).
In ``model 1``, the average displacement is assumed to scale linearly with the square root of the rupture area:

\begin{equation}
\bar{D} = c \sqrt{A} = c \sqrt{L~W} 
\end{equation}

in ``model 2``, the average displacement is assumed to scale linearly with the width of the rupture:

\begin{equation}
\bar{D} = c W
\end{equation}

while in ``model 3``, the average displacement is assumed to scale linearly with the length of the rupture:

\begin{equation}
\bar{D} = c L
\end{equation}

The three candidate models will be evaluated against the empirical data to decide which is best. 
Using ``model 1`` the $\mathbf{M}$ scaling relationship becomes:
\begin{equation}
\mathbf{M} = \log(L) + \log(W) + c
\end{equation}
with ``model 2`` the $\mathbf{M}$ scaling relationship becomes: 
\begin{equation}
\mathbf{M} = \frac{2}{3}\log(L) + \frac{4}{3}\log(W) + c
\end{equation}
and with ``model 3`` the $\mathbf{M}$ scaling relationship becomes: 
\begin{equation}
\mathbf{M} = \frac{4}{3}\log(L) + \frac{2}{3}\log(W) + c
\end{equation}

Substituting the ``model w1`` from the SCEC rupture simulations, for ``model 1`` we get: 
\begin{equation}
\mathbf{M} = \log(L) + \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})) + c
\end{equation}
for ``model 2`` we get:
\begin{equation}
\mathbf{M} = \frac{2}{3}\log(L) + \frac{4}{3} \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})) + c
\end{equation}
and for ``model 3`` we get:
\begin{equation}
\mathbf{M} = \frac{4}{3}\log(L) + \frac{2}{3} \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})) + c
\end{equation}

Assuming the surface to sub-surface rupture length scaling is of the form $\log(SRL) = c_1 \log(L) + c$, substituting it to the previous equations, condensing the constants, and solving for $\log(SRL)$, for ``model 1`` we get:
\begin{equation}
\log(SRL) = c_1 \left( \mathbf{M} - \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})) \right) + c_2 = c_1 X_1 + c
\end{equation}
for ``model 2`` we get:
\begin{equation}
\log(SRL) = c_1 \left( \frac{3}{2} \mathbf{M} - 2 \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})) \right) + c_2 = c_1 X_2 + c
\end{equation}
and for ``model 3`` we get:
\begin{equation}
\log(SRL) = c_1 \left( \frac{3}{4} \mathbf{M} - \frac{1}{2} \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})) \right) + c_2 = c_1 X_2 + c
\end{equation}

The previous equations can be expressed as linear models with, $X_1 = \mathbf{M} - \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})$, $X_2 = \frac{3}{2} \mathbf{M} - 2 \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})$, and $X_3 = \frac{3}{4} \mathbf{M} - \frac{1}{2} \min(\beta_1 + \beta_2 \mathbf{M}, \log(W_{lim})$.


The effect of the style of faulting is also considered through the use of additive terms to account for differences in the static stress drop. 
The static stress drop is defined as:
\begin{equation}
\Delta \sigma = C \mu \frac{\bar{D}}{L_C}
\end{equation}
thus, in log scale, a shift in the stress drop will be accompanied by a linear shift in the average displacement ($\log(\bar{D}) = \log(\Delta \sigma) + const$), which, in turn, will shift the intercept of the $SLR \sim \mathbf{M}$ models  
Two modeling approaches were evaluated: (i) a common additive term for dip-slip events ($F_D$), and (ii) separate additive terms for Normal and Reverse faults ($F_N$ and $F_R$). 
The style of faulting dependence introduced through $F_D$, $F_N$, and $F_R$ acts in addition to the style of faulting dependence introduced by the different dip angles between the different styles of faulting. 

The final regression relationship for ``model 1`` is:
\begin{equation}
\log(SRL) = c_1 X_1 + c_2 F_D + c_3
\end{equation}
the final regression relationship for ``model 2`` is:
\begin{equation}
\log(SRL) = c_1 X_2 + c_2 F_D + c_3
\end{equation}
the final regression relationship for ``model 3`` is:
\begin{equation}
\log(SRL) = c_1 X_3 + c_2 F_D + c_3
\end{equation}
and the final regression for separate additive terms with $D \sim \sqrt{A}$ scaling, hereafter denoted as ``model 1alt`` is:
\begin{equation}
\log(SRL) = c_1 X_1 + c_2 F_N + c_3 F_R + c_4
\end{equation}
Lastly a Wells and Coppersmith type model was also evaluated, hereafter referred as ``model 0``, to investigate the impact of width-limited ruptures on current state-of-practice models. 
\begin{equation}
\log(SRL) = c_1 \mathbf{M} + c_2 F_D + c_3
\end{equation}

The coefficients of the previous equations are estimated through a maximum likelihood regression. 

### Surface Rupture Length Modeling Based on Empirical Data

The five candidate models where were evaluated in predicting $SRL$ as a function of $\mathbf{M}$  are summarized in Table 4.


```{r, tab4, echo=FALSE}
df <- data.frame(model_name = c("model 0","model 1","model 2","model 3", "model 1 alt"),
                 model_fun  = c("$\\log(SLR)\\sim 1 + \\mathbf{M} + F_D$","$\\log(SLR)\\sim1 + X_1 + F_D$","$\\log(SLR)\\sim 1+X_2 + F_D$","$\\log(SLR)\\sim 1+X_3 + F_D$","$\\log(SLR)\\sim1 + X_1 + F_N+F_R$"),
                 model_desc = c("W&C 94 type model",
                                "$\\bar{D} \\sim \\sqrt{A}$ type model with $F_D$ addative term",
                                "$\\bar{D} \\sim {W}$ type model with $F_D$ addative term",
                                "$\\bar{D} \\sim {L}$ type model with $F_D$ addative term",
                                "$\\bar{D} \\sim \\sqrt{A}$ type model with $F_N$ & $F_R$ addative terms"))
kable(df, col.names = c("Name", "Functional Form", "Description"),  caption = "Table 4. Candiate Regression Models") %>%
  kable_styling(latex_options = "hold_position")
```

The next part shows the definition of the regression functional forms and model fit.

```{r srl_model_mag_regression}
# Rupture Width Modeling
#rupture width coefficients
c1_rw <- df_SCEC_model_width_mag_coeffs['model_w1','intrcp']
c2_rw <- df_SCEC_model_width_mag_coeffs['model_w1','M']
#compute rupture widths 
df_FDHI_srl$rup_width_unbnd <- 10^(c1_rw + c2_rw*df_FDHI_srl$magnitude)
df_FDHI_srl$rup_width <- pmin(df_FDHI_srl$rup_width_unbnd, df_FDHI_srl$seis_width)

#identify width limited events
df_FDHI_srl$flag_wlim <- FALSE
df_FDHI_srl[df_FDHI_srl$rup_width >= df_FDHI_srl$seis_width,'flag_wlim'] <- TRUE 


# SRL Modeling
#scaling parameters
df_FDHI_srl$x1 <-     df_FDHI_srl$magnitude -   log10(df_FDHI_srl$rup_width)
df_FDHI_srl$x2 <- 3/2*df_FDHI_srl$magnitude - 2*log10(df_FDHI_srl$rup_width)
df_FDHI_srl$x3 <- 3/4*df_FDHI_srl$magnitude - 1/2*log10(df_FDHI_srl$rup_width)
#standard deviation weights
width_scl <- 0.1
sig_scl   <- 2.
df_FDHI_srl$reg_wt <- ( 1 + (sig_scl-1) * sigmoid( 2.197225 * (log10(df_FDHI_srl$rup_width_unbnd)-log10(df_FDHI_srl$seis_width))/ width_scl ) )^2

## Regression formulas
form_model_srl0m     <- log10(event_len) ~ 1 + magnitude + FD
form_model_srl1m     <- log10(event_len) ~ 1 + x1 + FD
form_model_srl2m     <- log10(event_len) ~ 1 + x2 + FD
form_model_srl3m     <- log10(event_len) ~ 1 + x3 + FD
form_model_srl1m_alt <- log10(event_len) ~ 1 + x1 + FN + FR

## Regression
fit_model_srl0m     <- lm(form_model_srl0m,     data=df_FDHI_srl)
fit_model_srl1m     <- lm(form_model_srl1m,     data=df_FDHI_srl, weights=reg_wt)
fit_model_srl2m     <- lm(form_model_srl2m,     data=df_FDHI_srl, weights=reg_wt)
fit_model_srl3m     <- lm(form_model_srl3m,     data=df_FDHI_srl, weights=reg_wt)
fit_model_srl1m_alt <- lm(form_model_srl1m_alt, data=df_FDHI_srl, weights=reg_wt)
```

The print out below summarizes the log-likelihood and Akaike Information Criterion (AIC) for the different candidate models, while Table 5 summarizes the estimated coefficients. 
From a statistical perspective, ``model 1`` and ``model 2`` have similar good predictive performance, with Model 1 being slightly better, ``model 3`` has poorer performance, and ``model 0`` is the worst. 
``model 0`` does not consider the finite thickness of the seismogenic zone showcasing the limitations of a purely empirical model. 
``model 1`` to ``model 3`` have a break in the magnitude scaling when the width of the rupture reaches the width of the seismogenic zone allowing them to better fit the data.
From seismological theory, ``model 1`` and ``model 2`` should have unit slopes with respect to $X_1$ and $X_2$, if the subsurface rupture length ($L$) was the response variable.
Acknowledging the difference in the response variable, ``model 1`` is preferred as it is closer to the theoretical slope. 
In log-scale, any scalar difference between $SLR$ and $L$ would affect the constant.

```{r, srl_model_mag_summary, echo=FALSE}
#residuals
df_FDHI_srl$srl0m_res     <- resid(fit_model_srl0m)
df_FDHI_srl$srl1m_res     <- resid(fit_model_srl1m)
df_FDHI_srl$srl2m_res     <- resid(fit_model_srl2m)
df_FDHI_srl$srl3m_res     <- resid(fit_model_srl3m)
df_FDHI_srl$srl1m_alt_res <- resid(fit_model_srl1m_alt)

#coefficients
df_model_srl_mag_coef <-                                  as.data.frame(t(coef(fit_model_srl0m)),     row.names='model_srl0')
df_model_srl_mag_coef <- bind_rows(df_model_srl_mag_coef, as.data.frame(t(coef(fit_model_srl1m)),     row.names='model_srl1'))
df_model_srl_mag_coef <- bind_rows(df_model_srl_mag_coef, as.data.frame(t(coef(fit_model_srl2m)),     row.names='model_srl2'))
df_model_srl_mag_coef <- bind_rows(df_model_srl_mag_coef, as.data.frame(t(coef(fit_model_srl3m)),     row.names='model_srl3'))
df_model_srl_mag_coef <- bind_rows(df_model_srl_mag_coef, as.data.frame(t(coef(fit_model_srl1m_alt)), row.names='model_srl1_alt'))
df_model_srl_mag_coef['model_srl0','sigma']     <- sigma(fit_model_srl0m)
df_model_srl_mag_coef['model_srl1','sigma']     <- sigma(fit_model_srl1m)
df_model_srl_mag_coef['model_srl2','sigma']     <- sigma(fit_model_srl2m)
df_model_srl_mag_coef['model_srl3','sigma']     <- sigma(fit_model_srl3m)
df_model_srl_mag_coef['model_srl1_alt','sigma'] <- sigma(fit_model_srl1m_alt)
#rename columns
colnames(df_model_srl_mag_coef)[colnames(df_model_srl_mag_coef)=='(Intercept)'] <- 'intrcp'
colnames(df_model_srl_mag_coef)[colnames(df_model_srl_mag_coef)=='magnitude']   <- 'M'
colnames(df_model_srl_mag_coef)[colnames(df_model_srl_mag_coef)=='x1']          <- 'X1'
colnames(df_model_srl_mag_coef)[colnames(df_model_srl_mag_coef)=='x2']          <- 'X2'
colnames(df_model_srl_mag_coef)[colnames(df_model_srl_mag_coef)=='x3']          <- 'X3'
#reorder model coefficients
df_model_srl_mag_coef <- df_model_srl_mag_coef[,c('intrcp','M','X1','X2','X3','FD','FN','FR','sigma')]

## Prediction
#initialize dataframe
df_predict_srl_mag <- data.frame(magnitude=linspace(5, 8.5, 100))
#style of faulting
df_predict_srl_mag$FN <- 0
df_predict_srl_mag$FR <- 0
df_predict_srl_mag$FD <- 0
#rupture width unbounded 
df_predict_srl_mag$rup_width_unbnd <- 10^(c1_rw + c2_rw*df_predict_srl_mag$magnitude)

#predictions
#model 0
df_predict_srl_mag$srl0m_d   <- 10^( predict(fit_model_srl0m, df_predict_srl_mag) )
#models 1, 1alt, and 2
#15km seis width
df_predict_srl_mag$x1           <- df_predict_srl_mag$magnitude - pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(15))
df_predict_srl_mag$x2           <- 3/2*df_predict_srl_mag$magnitude - 2*pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(15)) 
df_predict_srl_mag$x3           <- 3/4*df_predict_srl_mag$magnitude - 1/2*pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(15)) 
df_predict_srl_mag$srl1m_d1     <- 10^( predict(fit_model_srl1m,     df_predict_srl_mag) )
df_predict_srl_mag$srl2m_d1     <- 10^( predict(fit_model_srl2m,     df_predict_srl_mag) )
df_predict_srl_mag$srl3m_d1     <- 10^( predict(fit_model_srl3m,     df_predict_srl_mag) )
df_predict_srl_mag$srl1m_alt_d1 <- 10^( predict(fit_model_srl1m_alt, df_predict_srl_mag) )
#20km seis width
df_predict_srl_mag$x1           <- df_predict_srl_mag$magnitude - pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(20))
df_predict_srl_mag$x2           <- 3/2*df_predict_srl_mag$magnitude - 2*pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(20)) 
df_predict_srl_mag$x3           <- 3/4*df_predict_srl_mag$magnitude - 1/2*pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(20)) 
df_predict_srl_mag$srl1m_d2     <- 10^( predict(fit_model_srl1m, df_predict_srl_mag) )
df_predict_srl_mag$srl2m_d2     <- 10^( predict(fit_model_srl2m, df_predict_srl_mag) )
df_predict_srl_mag$srl3m_d2     <- 10^( predict(fit_model_srl3m, df_predict_srl_mag) )
df_predict_srl_mag$srl1m_alt_d2 <- 10^( predict(fit_model_srl1m_alt, df_predict_srl_mag) )
#20km seis width and dip-slip
df_predict_srl_mag$x1           <- df_predict_srl_mag$magnitude - pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(15/sin(deg2rad(45))) )
df_predict_srl_mag$x2           <- 3/2*df_predict_srl_mag$magnitude - 2*pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(15/sin(deg2rad(45))) ) 
df_predict_srl_mag$x3           <- 3/4*df_predict_srl_mag$magnitude - 1/2*pmin(log10(df_predict_srl_mag$rup_width_unbnd), log10(15/sin(deg2rad(45))) ) 
df_predict_srl_mag$FD <- 1
df_predict_srl_mag$srl1m_d1FD   <- 10^( predict(fit_model_srl1m, df_predict_srl_mag) )
df_predict_srl_mag$srl2m_d1FD   <- 10^( predict(fit_model_srl2m, df_predict_srl_mag) )
df_predict_srl_mag$srl3m_d1FD   <- 10^( predict(fit_model_srl3m, df_predict_srl_mag) )

#sigma
df_predict_srl_mag$srl1m_d1_sig <- sigma(fit_model_srl1m) / ( 1 + (sig_scl-1) * sigmoid( 2.197225 * (log10(df_predict_srl_mag$rup_width_unbnd)-log10(15))/ width_scl ) )
df_predict_srl_mag$srl1m_d2_sig <- sigma(fit_model_srl1m) / ( 1 + (sig_scl-1) * sigmoid( 2.197225 * (log10(df_predict_srl_mag$rup_width_unbnd)-log10(20))/ width_scl ) )
#remove columns
df_predict_srl_mag <- subset(df_predict_srl_mag, select=-x1)
df_predict_srl_mag <- subset(df_predict_srl_mag, select=-x2)
df_predict_srl_mag <- subset(df_predict_srl_mag, select=-FN)
df_predict_srl_mag <- subset(df_predict_srl_mag, select=-FR)
df_predict_srl_mag <- subset(df_predict_srl_mag, select=-FD)

## Comparison of different models
fprintf('SRL Modeling:
        \tModel0:\n\t\tLogLik: %.2f\n\t\tAIC: %.2f\n 
        \tModel1:\n\t\tLogLik: %.2f\n\t\tAIC: %.2f\n
        \tModel2:\n\t\tLogLik: %.2f\n\t\tAIC: %.2f\n
        \tModel3:\n\t\tLogLik: %.2f\n\t\tAIC: %.2f\n
        \tModel1 alt.:\n\t\tLogLik: %.2f\n\t\tAIC: %.2f\n\n',
        logLik(fit_model_srl0m), AIC(fit_model_srl0m),
        logLik(fit_model_srl1m), AIC(fit_model_srl1m),
        logLik(fit_model_srl2m), AIC(fit_model_srl2m),
        logLik(fit_model_srl3m), AIC(fit_model_srl3m),
        logLik(fit_model_srl1m_alt), AIC(fit_model_srl1m_alt))

#empirical sigma below and above width threshold of model 1
sig_m1_wu <- sqrt(mean(df_FDHI_srl[!df_FDHI_srl$flag_wlim,'srl1m_res']^2))
sig_m1_wl <- sqrt(mean(df_FDHI_srl[ df_FDHI_srl$flag_wlim,'srl1m_res']^2))
fprintf('Standard Deviations:\n\tModel 1:\n\t\tEmpirical ratio for std of width limted to unbounded events is: %.2f',sig_m1_wu/sig_m1_wl)

#save SRL regression coefficients
write.csv(df_model_srl_mag_coef,  file=file.path(dir_out, 'model_coeffs_srl_mag.csv'))

summary(fit_model_srl1m)
```


```{r, srl_model_mag_coeffs, echo=FALSE}
#coefficients
kable(df_model_srl_mag_coef, 
      col.names = c('Intercept','$\\mathbf{M}$ scaling','$X_1$ scaling','$X_2$ scaling','$X_3$ scaling','$F_N$','$F_R$','$F_D$','$\\sigma$'),  
      caption = "Table 5. SRL Model Coefficients") %>%
  kable_styling(latex_options = "hold_position")
```

Figure 6 presents the predictions of all candidate $SRL$ models for Strike-slip events with a $15 km$ and $20 km$ width of seismogenic zone.

```{r fig_model_srl_mag, echo=FALSE, fig.cap="Figure 6. Prediction of candidate SRL Models for Strike-slip events with a 15km and 20km width of seismogenic zone"}
pl_model_srl_mag <- ggplot() + geom_point(data=df_FDHI_srl, aes(x=magnitude, event_len), color='black') +
                               geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl0m_d,      color=as.factor('Model 0: WC type')),             size=0.8) +
                               geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d1,     color=as.factor('Model 1: D~sqrt(A), FD')),       size=0.8) +
                               geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d2,     color=as.factor('Model 1: D~sqrt(A), FD')),       size=0.8, linetype="dashed") +
                               geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl2m_d1,     color=as.factor('Model 2: D~W, FD')),             size=0.8) +
                               geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl2m_d2,     color=as.factor('Model 2: D~W, FD')),             size=0.8, linetype="dashed") +
                               geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl3m_d1,     color=as.factor('Model 3: D~L, FD')),             size=0.8) +
                               geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl3m_d2,     color=as.factor('Model 3: D~L, FD')),             size=0.8, linetype="dashed") +
                               scale_color_brewer(palette="Set1") +
                               scale_y_log10(breaks=trans_breaks("log10", function(x) 10^x), labels=trans_format("log10", math_format(10^.x))) +
                               annotation_logticks(sides = "y") + labs(x='Magnitude', y='Surface Rupture Length (km)',
                                                                       color='Model') + 
                               theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                     axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                     legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))


pl_model_srl_mag
```

Figure 7 presents the predictions of ``model 1`` (preferred model) for the same Strike-slip events with a $15 km$ and $20 km$ width of seismogenic zone.

```{r fig_model_srl_mag_pref, echo=FALSE, fig.cap="Figure 7. Prediction of preferred SRL Model for Strike-slip events with a 15km and 20km width of seismogenic zone"}
df_FDHI_srl4plot <- subset(df_FDHI_srl, sof==0 & seis_depth<25)
df_FDHI_srl4plot$bin_w <- 0
df_FDHI_srl4plot[df_FDHI_srl4plot$seis_depth<=17.5,'bin_w'] <- 1
df_FDHI_srl4plot[df_FDHI_srl4plot$seis_depth>17.5,'bin_w'] <- 2
df_FDHI_srl4plot$bin_w <- as.factor(df_FDHI_srl4plot$bin_w)

pl_model_srl_mag_pref <- ggplot() + geom_point(data=df_FDHI_srl4plot, aes(x=magnitude, event_len, color=style2, size=style2, shape=bin_w)) +
                                    geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d1, linetype=as.factor(1)), size=0.8) +
                                    geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d2, linetype=as.factor(2)), size=0.8) +
                                    scale_color_manual(values=color_sof, breaks=c("Normal","Reverse","Strike-Slip")) +
                                    scale_size_manual(values=c(1.4,2,2.4), breaks=c("Normal","Reverse","Strike-Slip")) +
                                    scale_shape_manual(values=c(16,17), labels=c("\u2264 17.5 km","> 17.5 km")) +
                                    scale_linetype_manual(values=c('solid','dashed'), breaks=as.factor(c(1,2)), labels=c('15 km','20 km')) +
                                    scale_y_log10(breaks=trans_breaks("log10", function(x) 10^x), labels=trans_format("log10", math_format(10^.x))) +
                                    annotation_logticks(sides = "l") + labs(x='Magnitude', y='Surface Rupture Length (km)',
                                                                            color='Fault Style', size='Fault Style',
                                                                            shape='Seismogenic\nWidth',
                                                                            linetype='') +
                                    theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title),
                                          axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                          legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

pl_model_srl_mag_pref
```

Figure 8 presents the predictions of ``model 1`` for Strike-slip and Dip-slip events with a  $15 km$ width of seismogenic zone.

```{r fig_model_srl_mag_pref_FD, echo=FALSE, fig.cap="Figure 8. Prediction of preferred SRL Model for Strike-slip and Dip-slip events and 15km width of seismogenic zone"}
pl_model_srl_mag_pref_FD <- ggplot() + geom_point(data=subset(df_FDHI_srl, sof>=0 & seis_depth<25), aes(x=magnitude, event_len, color=style2, size=style2)) +
                                    geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d1,   linetype=as.factor(1)), size=0.8) +
                                    geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d1FD, linetype=as.factor(2)), size=0.8) +
                                    scale_color_manual(values=color_sof, breaks=c("Normal","Reverse","Strike-Slip")) +
                                    scale_size_manual(values=c(1.4,2,2.4), breaks=c("Normal","Reverse","Strike-Slip")) +
                                    scale_linetype_manual(values=c('solid','dotdash'), breaks=as.factor(c(1,2)), labels=c('Strike-Slip','Reverse')) +
                                    scale_y_log10(breaks=trans_breaks("log10", function(x) 10^x), labels=trans_format("log10", math_format(10^.x))) +
                                    annotation_logticks(sides = "y") + labs(x='Magnitude', y='Surface Rupture Length (km)',
                                                                            color='Fault Style', size='Fault Style',
                                                                            linetype='Model') +
                                    theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                          axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                          legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

pl_model_srl_mag_pref_FD

```

Figure 9 compares the predictions of ``model 0`` and ``model 1`` for Strike-slip events with a $15 km$ and $20 km$ width of seismogenic zone.
Both models have similar scaling for unbounded ruptures, but ``model 1`` also captures the change in scaling for width-limited ruptures leading to an overall better predictive performance. 

```{r fig_model_srl_mag_wlim, echo=FALSE, fig.cap="Figure 9. Prediction of Candidate SRL Models for Strike-slip events with a 15km and 20km width of seismogenic zone. Comparison with unbounded and width-limited events"}

pl_model_srl_mag_wlim <- ggplot() + geom_point(data=df_FDHI_srl, aes(x=magnitude, event_len, color=flag_wlim, shape=flag_wlim), size=2) +
                                    geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl0m_d,      linetype=as.factor(0)),       size=0.8) +
                                    geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d1,     linetype=as.factor(1)), size=0.8) +
                                    geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d2,     linetype=as.factor(1)), size=0.8) +
                                    scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                                    scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                                    scale_linetype_manual(values=c('dashed','solid'), breaks=c(as.factor(0), as.factor(1)),
                                                          labels=c('Model 0\nWC type', 'Model 1\nD~sqrt(A)')) +
                                    scale_y_log10(breaks=trans_breaks("log10", function(x) 10^x), labels=trans_format("log10", math_format(10^.x))) +
                                    annotation_logticks(sides = "l") + labs(x='Magnitude', y='Surface Rupture Length (km)',
                                                                            linetype='Model', color='Events', shape='Events') + 
                                    theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                          axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                          legend.title=element_text(size=size_text), legend.text=element_text(size=size_text, margin = margin(t = 2)))

pl_model_srl_mag_wlim
```

Figure 10 presents the regression residuals versus $\mathbf{M}$ for all candidate $SRL$ models.

```{r fig_models_srl_res_mag, echo=FALSE, fig.cap="Figure 10. Comparison Residuals of all candidate Models"}
pl_model_srl_res_mag <- ggplot() + geom_point(data=df_FDHI_srl, aes(x=magnitude, y=srl0m_res,     color=as.factor('Model 0: WC type'))) +
                                   geom_point(data=df_FDHI_srl, aes(x=magnitude, y=srl1m_res,     color=as.factor('Model 1: D~sqrt(A)'))) +
                                   geom_point(data=df_FDHI_srl, aes(x=magnitude, y=srl2m_res,     color=as.factor('Model 2: D~W'))) +
                                   geom_point(data=df_FDHI_srl, aes(x=magnitude, y=srl3m_res,     color=as.factor('Model 3: D~L'))) +
                                   annotation_logticks(sides = "l") + labs(x='Magnitude', y='Surface Rupture Length Residuals', color='Model') + 
                                   scale_color_brewer(palette="Set1") + ylim(-.8, 0.8) +
                                   theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                         axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                         legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))
pl_model_srl_res_mag
```

Figure 11 shows the ``model 0`` regression residuals versus magnitude.

```{r fig_model0_srl_res_mag, echo=FALSE, fig.cap="Figure 11. Linear model (Model 0, WC type) Residuals versus Magnitude"}
pl_model_srl_res_mag_m0 <- ggplot(data=df_FDHI_srl, aes(x=magnitude, y=srl0m_res)) + 
                           geom_point(aes(color=flag_wlim, shape=flag_wlim), size=2) +
                           geom_hline(yintercept=0,linetype="dashed") +
                           scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                           scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                           annotation_logticks(sides = "y") + labs(x='Magnitude', y='Surface Rupture Length Residuals', 
                                                                   linetype='Model', color='Events', shape='Events') +
                           scale_y_continuous(breaks=c(-0.75,-0.5,-0.25,0,0.25,0.5,0.75), limits=c(-0.8,0.8)) + 
                           theme(legend.position = c(0.75, 0.85), legend.background = element_rect(size=0.1, linetype="solid", colour='black')) +
                           theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                 axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                 legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

pl_model_srl_res_mag_m0
```

Figure 12 shows the ``model 1`` regression residuals versus magnitude.

```{r fig_model1_srl_res_mag, echo=FALSE, fig.cap="Figure 12. Prefered Model (Model 1, D~sqrt(A)) Residuals versus Magnitude"}
pl_model_srl_res_mag_m1 <- ggplot(data=df_FDHI_srl, aes(x=magnitude, y=srl1m_res)) + 
                           geom_point(aes(color=flag_wlim, shape=flag_wlim), size=2) +
                           geom_hline(yintercept=0,linetype="dashed") +
                           scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                           scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                           annotation_logticks(sides = "y") + labs(x='Magnitude', y='Surface Rupture Length Residuals', 
                                                                   linetype='Model', color='Events', shape='Events') +
                           scale_y_continuous(breaks=c(-0.75,-0.5,-0.25,0,0.25,0.5,0.75), limits=c(-0.8,0.8)) + 
                           theme(legend.position = c(0.85, 0.15), legend.background = element_rect(size=0.1, linetype="solid", colour='black')) +
                           theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                 axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                 legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

pl_model_srl_res_mag_m1
```


Figure 13 shows the ``model 2`` regression residuals versus magnitude.

```{r fig_model2_srl_res_mag, echo=FALSE, fig.cap="Figure 13. Prefered Model (Model 2, D~W) Residuals versus Magnitude"}
pl_model_srl_res_mag_m2 <- ggplot(data=df_FDHI_srl, aes(x=magnitude, y=srl2m_res)) + 
                           geom_point(aes(color=flag_wlim, shape=flag_wlim), size=2) +
                           geom_hline(yintercept=0,linetype="dashed") +
                           scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                           scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                           annotation_logticks(sides = "y") + labs(x='Magnitude', y='Surface Rupture Length Residuals', 
                                                                   linetype='Model', color='Events', shape='Events') +
                           scale_y_continuous(breaks=c(-0.75,-0.5,-0.25,0,0.25,0.5,0.75), limits=c(-0.8,0.8)) + 
                           theme(legend.position = c(0.85, 0.15), legend.background = element_rect(size=0.1, linetype="solid", colour='black')) +
                           theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                 axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                 legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

pl_model_srl_res_mag_m2
```


Figure 14 shows the ``model 3`` regression residuals versus magnitude.

```{r fig_model3_srl_res_mag, echo=FALSE, fig.cap="Figure 14. Prefered Model (Model 3, D~L) Residuals versus Magnitude"}
pl_model_srl_res_mag_m3 <- ggplot(data=df_FDHI_srl, aes(x=magnitude, y=srl3m_res)) + 
                           geom_point(aes(color=flag_wlim, shape=flag_wlim), size=2) +
                           geom_hline(yintercept=0,linetype="dashed") +
                           scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                           scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                           annotation_logticks(sides = "y") + labs(x='Magnitude', y='Surface Rupture Length Residuals', 
                                                                   linetype='Model', color='Events', shape='Events') +
                           scale_y_continuous(breaks=c(-0.75,-0.5,-0.25,0,0.25,0.5,0.75), limits=c(-0.8,0.8)) + 
                           theme(legend.position = c(0.85, 0.15), legend.background = element_rect(size=0.1, linetype="solid", colour='black')) +
                           theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                 axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                 legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

pl_model_srl_res_mag_m3
```


A rupture-width transition parameter $\delta$ is defined as $\delta = \log_{10}(W_{unb}) - \log_{10}(W_{lim})$; $W_{unb}$ is the theoretical rupture width for an infinite seismogenic zone estimated from the first leg of `model w1` ($\log_{10}(W_{unb}) = \beta_1 \mathbf{M} + \beta_2$).
A negative value of $\delta$ corresponds to a unbounded rupture, whereas a positive corresponds to a width-limited rupture. 
Figure 15 shows the ``model 1`` regression residuals versus $\delta$. 
The solid black lines correspond to the rupture-width transition dependent standard deviation. 

```{r fig_model6_srl_res_width, echo=FALSE, fig.cap="Figure 15. Prefered Model (Model 1, D~sqrt(A)) Residuals versus Width transition"}
df_sig_model <- data.frame(delta_W = linspace(-1.25, 0.5))
df_sig_model$model0_sig <- df_model_srl_mag_coef['model_srl1','sigma'] / ( 1 + (sig_scl-1) * sigmoid( 2.197225 * (df_sig_model$delta_W)/ width_scl ) )

pl_model_srl_res_width_m1 <- ggplot(data=df_FDHI_srl, aes(x=log10(rup_width_unbnd)-log10(seis_width), y=srl1m_res)) + 
                             geom_point(aes(color=flag_wlim, shape=flag_wlim), size=2) +
                             geom_hline(yintercept=0,linetype="dashed") +
                             geom_line(data=df_sig_model, aes(x=delta_W, y= model0_sig, 
                                                                    linetype=as.factor('Mag Dependent\nStandard Dev')), size=0.8) +
                             geom_line(data=df_sig_model, aes(x=delta_W, y=-model0_sig), size=0.8) +
                             scale_shape_manual(values=shape_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                             scale_color_manual(values=color_width_flag, breaks=c(FALSE, TRUE), labels=c("Unbounded", "Width Limited")) +
                             annotation_logticks(sides = "x") + labs(x='Rupture Width Transition Parameter (\u03B4_W)', 
                                                                     y='Surface Rupture Length Residuals', 
                                                                     linetype=NULL, color='Events', shape='Events') +
                             scale_y_continuous(breaks=c(-0.75,-0.5,-0.25,0,0.25,0.5,0.75), limits=c(-0.8,0.8)) + 
                             theme(legend.position = c(0.73, 0.90), legend.box = "horizontal",
                                   legend.background = element_rect(size=0.1, linetype="solid", colour='black')) + guides(color="none", shape="none") +
                             theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                   axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                   legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))

show(pl_model_srl_res_width_m1)
```

```{r save_fig_model, echo=FALSE}
#save figures
#scaling
ggsave(file.path(dir_fig,'models_srl_mag_wlim.png'),    plot=pl_model_srl_mag_wlim,                                device='png', width=6.2, height=4)
ggsave(file.path(dir_fig,'models_srl_mag_pref.png'),    plot=pl_model_srl_mag_pref,                                device='png', width=5.9,   height=4)
ggsave(file.path(dir_fig,'models_srl_mag_pref_FD.png'), plot=pl_model_srl_mag_pref_FD,                             device='png', width=5.9,   height=4)
#residuals
ggsave(file.path(dir_fig,'model0_srl_res_mag.png'),    plot=pl_model_srl_res_mag_m0,                               device='png', width=4.5, height=4)
ggsave(file.path(dir_fig,'model1_srl_res_mag.png'),    plot=pl_model_srl_res_mag_m1+theme(legend.position="none"), device='png', width=4.5, height=4)
ggsave(file.path(dir_fig,'model2_srl_res_mag.png'),    plot=pl_model_srl_res_mag_m2+theme(legend.position="none"), device='png', width=4.5, height=4)
ggsave(file.path(dir_fig,'model3_srl_res_mag.png'),    plot=pl_model_srl_res_mag_m3+theme(legend.position="none"), device='png', width=4.5, height=4)
ggsave(file.path(dir_fig,'model1_srl_res_width.png'),  plot=pl_model_srl_res_width_m1, device='png', width=4.5, height=4)

```

### Comparison With Existing Models

Figure 16 compares the preferred model with existing $SLR$ relationships.
WC94 All and WC94 SS correspond to the Wells and Coppersmith (1994) $SRL ~ \mathbf{M}$ scaling relationships for All types of slip and Strike-slip events.
WY15 OLS and WY15 Deming correspond to the Wells and Youngs (2015) $SRL ~ \mathbf{M}$ scaling relationships using ordinary-least-squares and errors-in-variables regression models. 
L10 DS, L10 SS, and L10 SRC correspond to the Leonard (2010) $SRL ~ \mathbf{M}$ scaling relationships for Dip-slip, Strike-slip, and Stable-Continental events.
The proposed model is in agreement with the existing models over different magnitude ranges. 
It is in good agreement with the Leonard (2010) scaling relationship for small to moderate size events, and in good agreement with the Wells and Coppersmith (1994) and Wells and Youngs (2015) scaling relationships at large size events. 
A potential reason for the agreement at different magnitude ranges is that the dataset used by Leonard (2010) was primarily composed of events ranging from $\mathbf{M}~5$ to $7$, while datasets used by Wells and Coppersmith (1994) and  Wells and Youngs (2015) was primarily composed of events ranging from $\mathbf{M}~6$ to $7.8$.

```{r, srl_model_mag_cmp, echo=FALSE, fig.cap="Figure 16. Comparison Preferred Model (Model 1, D~sqrt(A)) with existing SLR relationships"}

## Prediction Existing Models
#initialize dataframe
df_other_models <- data.frame(magnitude=linspace(5, 8.5, 100))
#Wells and Coppersmith, 1994 (SRL vs mag)
df_other_models$srl_wc94_ss  <- 10^(-3.55 + 0.74 * df_other_models$magnitude)
df_other_models$srl_wc94_r   <- 10^(-2.86 + 0.63 * df_other_models$magnitude)
df_other_models$srl_wc94_n   <- 10^(-2.01 + 0.50 * df_other_models$magnitude)
df_other_models$srl_wc94_all <- 10^(-3.22 + 0.69 * df_other_models$magnitude)
#Wells and Youngs, 2015
df_other_models$srl_wy15_ols    <- 10^(-4.6478 + 0.9041 * df_other_models$magnitude)
df_other_models$srl_wy15_ols_a  <- 10^(-4.5780 + 0.8926 * df_other_models$magnitude)
df_other_models$srl_wy15_deming <- 10^(-3.8253 + 0.7830 * df_other_models$magnitude)
df_other_models$srl_wy15_n      <- 10^(-4.8011 + 0.9325 * df_other_models$magnitude)
df_other_models$srl_wy15_r      <- 10^(-4.2692 + 0.8410 * df_other_models$magnitude)
df_other_models$srl_wy15_ss     <- 10^(-4.8243 + 0.9330 * df_other_models$magnitude)
#Leonard 2010
df_other_models$srl_l10_ds  <- 10^( 1/1.52*(-4.40 + df_other_models$magnitude) )
df_other_models$srl_l10_ss  <- 10^( 1/1.52*(-4.33 + df_other_models$magnitude) )
df_other_models$srl_l10_src <- 10^( 1/1.67*(-4.32 + df_other_models$magnitude) )


#figures predictions
pl_model_cmp_m1 <- ggplot() + geom_line(data=df_other_models,    aes(x=magnitude, y=srl_wc94_all,    linetype=as.factor('Existing'), color=as.factor('WC94 All')),    size=0.8) +
                              geom_line(data=df_other_models,    aes(x=magnitude, y=srl_wc94_ss,     linetype=as.factor('Existing'), color=as.factor('WC94 SS')),     size=0.8) +
                              geom_line(data=df_other_models,    aes(x=magnitude, y=srl_wy15_ols,    linetype=as.factor('Existing'), color=as.factor('WY15 OLS')),    size=0.8) +
                              geom_line(data=df_other_models,    aes(x=magnitude, y=srl_wy15_deming, linetype=as.factor('Existing'), color=as.factor('WY15 Deming')), size=0.8) +
                              geom_line(data=df_other_models,    aes(x=magnitude, y=srl_l10_ds,      linetype=as.factor('Existing'), color=as.factor('L10 DS')),      size=0.8) +
                              geom_line(data=df_other_models,    aes(x=magnitude, y=srl_l10_ss,      linetype=as.factor('Existing'), color=as.factor('L10 SS')),      size=0.8) +
                              geom_line(data=df_other_models,    aes(x=magnitude, y=srl_l10_src,     linetype=as.factor('Existing'), color=as.factor('L10 SRC')),     size=0.8) +
                              geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d1, linetype=as.factor('New, Model 1')), size=0.8) +
                              geom_line(data=df_predict_srl_mag, aes(x=magnitude, y=srl1m_d2, linetype=as.factor('New, Model 1')), size=0.8) +
                              scale_y_log10(breaks=trans_breaks("log10", function(x) 10^x),  labels=trans_format("log10", math_format(10^.x)) ) +
                              scale_linetype_manual(values=c("dashed", "solid"))+
                              annotation_logticks(sides = "l") + labs(x='Magnitude', y='Surface Rupture Length (km)', color=NULL, linetype='Models') +
                              guides(colour = guide_legend(order = 2), linetype = guide_legend(order = 1)) +
                              theme(plot.title=element_text(size=size_title),  axis.title=element_text(size=size_title), 
                                    axis.text.y=element_text(size=size_text),  axis.text.x=element_text(size=size_text),
                                    legend.title=element_text(size=size_text), legend.text=element_text(size=size_text))
pl_model_cmp_m1

ggsave(file.path(dir_fig,'model1_srl_mag_cmp_existing_models.png'),  plot=pl_model_cmp_m1, device='png', width=6.2, height=4)
```


## Acknowledgements

* Alexandra Sarmiento (discussions & comments)
* Stephane Baize (data)


## References

Baize, S., O. Scotti, J.-F. Ritz, M. Ferry, C. Larroque, E. Mathot, L. Audin, F. Nurminen, P. Boncio, and B. Delouis (2020). Surface ruptures during moderate earthquakes: Is that so rare? Geological Society of America 2020 Connects Online

Bodin, P., and J. N. Brune (1996). On the scaling of slip with rupture length for shallow strike-slip earthquakes: Quasistatic models and dynamic rupture propagation, Bull. Seismol. Soc. Am. 86, 1292.

Hanks, T. C., & Bakun, W. H. (2002). A bilinear source-scaling model for M-log A observations of continental earthquakes. Bulletin of the Seismological Society of America, 92(5), 1841-1846.

Leonard, M. (2010). Earthquake fault scaling: Self-consistent relating of rupture length, width, average displacement, and moment release. Bulletin of the Seismological Society of America, 100(5A), 1971-1988.

Romanowicz, B. (1992). Strikeslip earthquakes on quasivertical transcurrent faults: Inferences for general scaling relations. Geophysical Research Letters, 19(5), 481-484.

Romanowicz, B. (1994). Comment on A reappraisal of large earthquake scaling by C. Scholz. Bulletin of the Seismological Society of America, 84(5), 1675-1676.

Romanowicz, B., & Rundle, J. B. (1993). On scaling relations for large earthquakes. Bulletin of the Seismological Society of America, 83(4), 1294-1297.

Pegler, G., & Das, S. (1996). Analysis of the relationship between seismic moment and fault length for large crustal strikeslip earthquakes between 197792. Geophysical research letters, 23(9), 905-908.

Scholz, C. H. (1982). Scaling laws for large earthquakes: consequences for physical models. Bulletin of the Seismological Society of America, 72(1), 1-14.

Scholz, C. H. (1994). A reappraisal of large earthquake scaling. Bulletin of the Seismological Society of America, 84(1), 215-218.

Scholz, C. H. (1997). Size distributions for large and small earthquakes. Bulletin of the Seismological Society of America, 87(4), 1074-1077.

Scholz, C. H. (1998). A further note on earthquake size distributions. Bulletin of the Seismological Society of America, 88(5), 1325-1326.

Wang, Y., & Goulet, C. (2021). Validation of fault displacements from dynamic rupture simulations against the observations from the 1992 landers earthquake. Bulletin of the Seismological Society of America, 111(5), 2574-2594.

Wells, D. L., & Coppersmith, K. J. (1994). New empirical relationships among magnitude, rupture length, rupture width, rupture area, and surface displacement. Bulletin of the seismological Society of America, 84(4), 974-1002.

Wells, D. L., & Youngs R. B.  (2015). Improved Regression Relations for Earthquake Source Parameters. Seismological Society of America 2015 Annual Meeting
